The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-02-28 main.tex
de-capitalize e.g.s

The \astropy Project is built on a philosophy of building from the existing
Python scientific ecosystem wherever possible. Many of the enabling technologies
like \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, or \texttt{cython},
are necessary as the core underpinnings of \astropy packages.  Often this means
using these packages as ``building blocks'' (E.g., the ubiquitous
use of \texttt{numpy} arrays throughout \astropypkg).  In other cases this means
wrappers around more general algorithms that make them more convenient for
astronomy use cases (E.g., the model-fitting in the \package{astropy.modeling}
subpackage discussed in \sectionname~\ref{sec:modeling}).  Sometimes these
simple wrappers evolve into more complex implementations that address
astronomically-relevant use cases the general tool does not support (E.g.,
\package{astropy.convolution}, see \sectionname~\ref{ssec:convolution}). As a
broad rule, the Project explicitly encourages re-use of code where possible.

However, the boundaries of when this re-use is called for often ambiguous.  Some
of the examples above only evolved after significant debate in the community
over whether these algorithms were sufficient.  Other times, even apparently
general functionality did not exist in the wider ecosystem that met the \astropy
community's needs, and hence the functionality had to be developed wholly from
the developer resources available in the community (E.g.,
\package{astropy.units}, or \package{astropy.table} when it began). While some
of this functionality is ``given back'' to the wider community (E.g., myriad bug
fixes for the enabling technologies listed above, and some of the testing and
documentation architecture), in general, careful consideration is taken of
whether the additional effort to make a piece of \astropy, and it is only
``extracted'' when it seems plausible that the ongoing effort is worth the
reward in the form of additional contributors or maintainers.

>>>>

The \astropy Project is built on a philosophy of building from the existing
Python scientific ecosystem wherever possible. Many of the enabling technologies
like \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, or \texttt{cython},
are necessary as the core underpinnings of \astropy packages.  Often this means
using these packages as ``building blocks'' (e.g., the ubiquitous
use of \texttt{numpy} arrays throughout \astropypkg).  In other cases this means
wrappers around more general algorithms that make them more convenient for
astronomy use cases (e.g., the model-fitting in the \package{astropy.modeling}
subpackage discussed in \sectionname~\ref{sec:modeling}).  Sometimes these
simple wrappers evolve into more complex implementations that address
astronomically-relevant use cases the general tool does not support (e.g.,
\package{astropy.convolution}, see \sectionname~\ref{ssec:convolution}). As a
broad rule, the Project explicitly encourages re-use of code where possible.

However, the boundaries of when this re-use is called for often ambiguous.  Some
of the examples above only evolved after significant debate in the community
over whether these algorithms were sufficient.  Other times, even apparently
general functionality did not exist in the wider ecosystem that met the \astropy
community's needs, and hence the functionality had to be developed wholly from
the developer resources available in the community (e.g.,
\package{astropy.units}, or \package{astropy.table} when it began). While some
of this functionality is ``given back'' to the wider community (e.g., myriad bug
fixes for the enabling technologies listed above, and some of the testing and
documentation architecture), in general, careful consideration is taken of
whether the additional effort to make a piece of \astropy, and it is only
``extracted'' when it seems plausible that the ongoing effort is worth the
reward in the form of additional contributors or maintainers.
